\input{../PyCharm_Beamer_Preamble.tex}
% !Tex spellceck = en_US

\title[MA Seminar Talk - Progress]{Master Thesis Seminar Talk}
\subtitle{Progress Upade}
\author[F. Beaumont]{Fabrice Beaumont}
\institute[]{Department of Information Systems and Artificial Intelligence - \textbf{Dr. Pascal Welke}}
\date{09. February 2022}
\begin{document}


\begin{frame}
	\titlepage
\end{frame}

\begin{frame}
\frametitle{Method overview} \vspace{-1cm}
	Ongoing tasks:
	\begin{enumerate}
		\item Writing an thesis exposé\\
		$\implies$ Formulating precise (initial) research questions.
	\end{enumerate}

	Basic idea and (re)opened questions:
	\begin{enumerate}
		\item Construct the Wl-labeling hierarchy tree $T$ on a set of graphs
		\item Initialize edge weights in $T$
		\item Refinement Loop:
		\begin{enumerate}
			\item \color{red}{Evaluate the performance of the edge weights.}\\
			Initial approach: Use the Wasserstein distance on vector representations of graphs. \color{red}{How to get a differentiated feedback for the weight adjustments?}
			\item \color{red}{(How to) Update the edge weights.}\\
			Initial approach: Static updates with fixed margin.
		\end{enumerate}
	\end{enumerate}
	\hfill\newline
	\begin{itemize}		
		\item[] \hfill\newline
		\item[] \hfill\newline
	\end{itemize}
\end{frame}

% 4 
\begin{frame}
\frametitle{Method overview} \vspace{-1cm}
\begin{enumerate}
	\item \begin{tabbing}
		Given: \=Graph database $\mathcal{D}=\{ (V_i, E_i, \ell^V_i) \}_{i\in[N]}$\\
		\>Distance $d$ on $\bigcup_{i\in[N]}\text{Range}(\ell^V_i)$\ \ \=for the FRM\\
		\>Ground distance $d_0$\>for the Wass.Dist. $W_{\text{WLT}}$
	\end{tabbing}
	\item Compute $t$ iterations of Weisfeiler Lehman (WL) labels on $\mathcal{D}$
	\item Construct the WL labeling tree (WLLT) [WL labeling hierarchy]
	\item Define edge weights on the WLLT - using a FRM (and $d$)		
	\item Define an \underline{initial} distance between graphs - using $W_{\text{WLT}}$ (and $d_0$)
\end{enumerate}
\textbf{Loop:}
\begin{itemize}		
	\item Use the distances to define a WWL-kernel and classify the database using an SVM
	\item Use the mapping chosen by $W_{\text{WLT}}$ to identify crucial edge weights. \textbf{Refine the edge weights}, given the desired closeness of the graphs.
\end{itemize}
\end{frame}

% 5
\begin{frame}
\frametitle{Current progress}
	Programming:
	\begin{itemize}
		\item Construction of the WL-labeling tree (WLLT) \newline
		\item Several distance metrics for this WLLT \newline
		\item Construction of the WL-label set representation of the graphs \newline
		\item Construction of a distance matrix/kernel on the dataset\newline
	\end{itemize}	
	Still in progress: Several optimizations w.r.t to these implementations.
\end{frame}

% 6
\begin{frame}
\frametitle{Next steps}
	\begin{itemize}
		\item Write an \textbf{exposé} to sketch and summarize these research plans \newline
		\item Implement the usage of the Wasserstein Distance\newline
		\item Chose (several?) update steps or learning methods to adjust the \textit{hot weights}. First:
		\begin{itemize}
			\item Constant update with a fixed margin $\eta$\newline
		\end{itemize}
		\item Implement a \textbf{feedback-system}. (An evaluation of the used weights) \newline
		\item Literature research
	\end{itemize}	
\end{frame}

\section{End}
\begin{frame}[c]
	\centering %\Huge
	\begin{huge}
		\emph{Thank you all for listening.}\\
	\end{huge}
	\vspace{2 cm}
	I will be happy to answer any \textbf{questions} and\\
	hear your \textbf{comments}.
\end{frame}

\end{document}